### 2016-01-21 AcademicPaperSummaries/PaperSummaries.tex
blomberg et al

Keywords provide a shorthand for broad type of paper (theory development, disaggregation, test theory, introduce data., literature review....); empirical approach (formal model, quant, computational)
Structure:
Citation
Research question and research area
Summary of argument and mechanism
Data \& methods
Findings
Notes on related papers

@@

>>>>

Keywords provide a shorthand for broad type of paper (theory development, disaggregation, test theory, introduce data., literature review....); empirical approach (formal model, quant, computational)

Structure and keywords:

Citation

\underline{Keywords:}

\underline{Research question and research area}
\underline{Summary of argument and mechanism}
\underline{Data \& methods}
\underline{Findings}
\underline{Notes on related papers}

@@

\textbf{Blomberg, S. Brock, Gregory D. Hess and Akila Weerapana. 2004. “Economic Conditions and Terrorism.” European Journal of Political Economy 20(2):463-478.}

\underline{Keywords:} quant; computational; theory testing.

Research question and research area: Blomberg et al. contribute to the literature on how economic conditions influence terrorist activities.
Terrorism definition: differentiate between ``rebellion'' which happens when a group that wants to change the status quo overthrows the government and takes power and ``terrorist attacks'' when dissident groups use ``terror activities'' to ``increase voice in economy'' but are not able to overthrow government. Note the almost tautological definition and the build-in assumption that terror attacks are intended to express a perspective on economy. Terror attacks conceptualized as ``low-intensity attacks'' designed to signal discontent with status quo. [This definition would include the far-left / far-right vandalism.]
\underline{Summary of argument and mechanism:} Groups choose between rebellion and terror attacks according to whether the country can give in to the dissidents. Strong institutions attracts terrorism; weak ones attract rebellion. [Observe that this outcome is built into their definition: weaker states should disproportionately attract attacks that threaten the state institutions because the institutions are more vulnerable.] They have a strong underlying assumption that attacks are intended to signal discontent. Assumption that attacks are either signals of anger or earnest attempts to overthrow government.
\underline{Data \& methods:} Dataset of 130 countries from 1968-1991, country-year unit of analysis. Data from ITERATE, which is transnational attacks and thus doesn't really match their theory, with economic indicators. Build a model of economic state change and terrorism/no terrorism through Markov processes. Do not appear to have any measure of the rebellion actions of their theory and look at conditional probabilities of state change. [Methodological question: are Markov chains at all appropriate for strategic interactions? In general, they are only applicable for linear systems.]
\underline{Findings:} In democratic, high income, countries, recessions increase probabilities of terror attacks. 
Notes on related papers:

\textbf{Chenoweth, Erica. 2013. “Terrorism and Democracy.” Annual Review of Political Science 16: 355–378.}

\underline{Keywords:}

\underline{Research question and research area}
\underline{Summary of argument and mechanism}
\underline{Data \& methods}
\underline{Findings}
\underline{Notes on related papers}
